Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-13 krs-survey.tex
Merged Dynamic Instantiation with Structural Alteration

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf C. Reasoning}
            child {node [taxon] {{\bf C.10}. Learning}}
            child {node [taxon] {{\bf C.9}. Naive physics}}
            child {node [taxon] {{\bf C.8}. Planning}}
            child {node [taxon] {{\bf C.7}. Prediction}}
            child {node [taxon] {{\bf C.6}. Presupposition}}
            child {node [taxon] {{\bf C.5}. Non-monotonicity}}
            child {node [taxon] {{\bf C.4}. Uncertainty}}
            child {node [taxon] {{\bf C.3}. Lazy evaluation}}
            child {node [taxon] {{\bf C.2}. Structural alteration}}
            child {node [taxon] {{\bf C.1}. Standard reasoning}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\subsubsection{Alteration of the knowledge structure}

@@

The terms TBox and ABox are commonly found to describe this two different types of
statements in ontologies. TBox statements describe a system in terms of
controlled vocabularies, for example, a set of classes and properties. ABox are
TBox-compliant statements about that vocabulary.

All knowledge representation systems allow to modify the ABox, which can be
considered as the dynamic part of the knowledge base. It is however not always
possible to alter the TBox because not all reasoning systems can dynamically
take into account structural changes in the knowledge base.

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf D. Acquisition}
            child {node [taxon] {{\bf D.4} Dynamic instantiation}}
            child {node [taxon] {{\bf D.3} Motivation}}
            child {node [taxon] {{\bf D.2} Grounding}}
            child {node [taxon] {{\bf D.1} Acquisition and fusion}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\subsubsection{Dynamic instantiation}
\label{sect|new-instances}
Ability to automatically create new object instances

>>>>

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf C. Reasoning}
            child {node [taxon] {{\bf C.10}. Learning}}
            child {node [taxon] {{\bf C.9}. Naive physics}}
            child {node [taxon] {{\bf C.8}. Planning}}
            child {node [taxon] {{\bf C.7}. Prediction}}
            child {node [taxon] {{\bf C.6}. Presupposition}}
            child {node [taxon] {{\bf C.5}. Non-monotonicity}}
            child {node [taxon] {{\bf C.4}. Uncertainty}}
            child {node [taxon] {{\bf C.3}. Lazy evaluation}}
            child {node [taxon] {{\bf C.2}. Instantiation and structural alteration}}
            child {node [taxon] {{\bf C.1}. Standard reasoning}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\subsubsection{Dynamic Instantiation and Alteration of the Knowledge Structure}

@@

The terms TBox and ABox are commonly found to describe this two different types of
statements in ontologies: TBox statements describe a system in terms of
controlled vocabularies, for example, a set of classes and properties. ABox are
TBox-compliant statements about that vocabulary.

Most knowledge representation systems allow to modify the ABox, which can be
considered as the dynamic part of the knowledge base. Alteration of the ABox
include the addition or retractation of relations between existing instances,
and the addition or removal of instances. We call the later \emph{dynamic
instantiation}: the capability for a system to create new instances at
run-time. The term dynamic instantion applies primarily to concrete entities
(typically, a new object is discovered by the robot, a symbolic instance is
created for it), but may also apply to abstract entities (like an instance of
action, of a feeling, etc.).

KRS may also allow to alter the TBox. This requires the underlying reasoning
systems to be able to dynamically take into account structural changes in the
knowledge base.

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf D. Acquisition}
            child {node [taxon] {{\bf D.3} Motivation}}
            child {node [taxon] {{\bf D.2} Grounding}}
            child {node [taxon] {{\bf D.1} Acquisition and fusion}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@
